\section{Bibliografie}
\begingroup
\renewcommand{\section}[2]{}
\begin{thebibliography}{1}

\bibitem{alexnet} Alex Krizhevsky, Ilya Sutskever, Geoffrey E. Hinton {\em ImageNet Classification with Deep Convolutional Neural Networks}  2012.

\bibitem{lenet} Yann LeChun, Leon Bottou, Yoshua Bengio, Patrick Haffner {\em Gradient-Based Learning Applied to Document Recognition} 1998.

\bibitem{multiInstance} Jaume Amores {\em Multiple Instance Classification: review, taxonomy and
comparative study} \\
Computer Vision Center, Computer Science Department, UAB, Spain 2013.

\bibitem{vgg16} Karen Simonyan, Andrew Zisserman {\em Very deep convolutional networks for large-scale image recognition} 2015.

\bibitem{resnet}  Kaiming He, Xiangyu Zhang,  Shaoqing Ren, Jian Sun {\em Deep Residual Learning for Image Recognition} \\
Microsoft Research, 2015.

\bibitem{inception} Christian Szegedy, Wei Liu, Yangqing Jia, Pierre Sermanet, Scott Reed, Dragomir Anguelov, Dumitru Erhan, Vincent Vanhoucke, Andrew Rabinovich {\em Going deeper with convolutions} 2014.

\bibitem{xception} Francois Chollet {\em Xception: Deep Learning with Depthwise Separable Convolutions} 2017.

\bibitem{featureExtraction} Lars Hertel, Erhardt Barth, Thomas Käster, Thomas Martinetz {\em Deep Convolutional Neural Networks as Generic Feature Extractors} \\
Institute for Signal Processing, University of Luebeck, Germany \\
Institute for Neuro- and Bioinformatics, University of Luebeck, Germany.

\bibitem{featureRep} Ben Athiwaratkun, Keegan Kang {\em Feature Representation In Convolutional Neural
Networks} \\
Department of Statistical Science Cornell University 2015.

\bibitem{adam} Diederik P. Kingma, Jimmy Lei Ba, {\em ADAM: A METHOD FOR STOCHASTIC OPTIMIZATION} \\
University of Amsterdam, OpenAI 2017\\
University of Toronto 2017.

\bibitem{rmsprop} Geoffrey Hinton {\em Neural Networks for Machine Learning: Lecture 6a	Overview of	mini-batch gradient descent	}

\bibitem{deeplearningAI} \texttt{https://www.coursera.org/learn/neural-networks-deep-learning}

\bibitem{competition} \texttt{https://www.kaggle.com/c/yelp-restaurant-photo-classification}

\end{thebibliography}
\endgroup